Open-source landscape for 3D CSEM modelling

### 2020-10-02 manuscript/Manuscript.tex
Incorporated all suggestions and ideas from Raphael.

The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well log data a realistic, three-dimensional resistivity model with vertical transverse isotropy (VTI), called MR3D, which they released under the open creative common license \emph{CC BY 4.0}. \cite{GEO.19.Correa} computed CSEM data for MR3D for six frequencies from 0.125\,Hz to 1.25\,Hz, and released them under the same CC license. To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}. It is therefore an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code. Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.

@@

The responses for all six frequencies, both inline and broadside, for all three electric components are shown in Figure~\ref{fig:results-marlim-responses}. The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two datasets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree very well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
\begin{enumerate}
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components. The differences are related to the bathymetry. And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here.
\end{enumerate}

Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
%
\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively. Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
%
A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less, particularly for the inline $E_x$ component it is only a few \% or less. In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., negative offsets in the inline and broadside $E_x$ responses, in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD. Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.

\imycom[RR]{The following paragraph is rather discussion content. Before, we mainly restricted to show data only with observations, I would keep this style also here}
One might argue that 5-10\,\% NRMSD is a lot. We argue that this is probably as good as it gets, given that the code with which we compare is not open-source. This has been shown within the process of these results. Our first attempt were based on the originally published, fine MR3D model. This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation. However, none of the codes were able to reproduce the published results. The reason is that there are many ways how you can extrapolate a model. We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model. It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.

\imycom[RR]{Mostlyx redundant content to the information introduced before, I think this paragraph can be removed compeltely}
However, even though the computational input model is know, we still do not know what the code SBLwiz exactly does inside. From the information we have we know that it computes the data in the time domain transforming them afterwards to the frequency domain, and it includes the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}. All our codes, on the other hand, compute in the frequency domain and include the air layer in the model (putting the boundaries sufficiently far away).

@@

The differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
%
\plot*{results-marlim_entire}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the entire computational domain.}
%
The top rows show the tensor mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem. The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.
\itodo{Write more once the other results are in the figures too. Points to compare: See if the different boundary conditions are visible. See and comment on the effects of the different, fast coarsening outside the domain of interest.}
%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
%
\itodo{Most importantly, once all results are in the figures: Discuss about the effect of bathymetry, particularly on the $E_y$ field. Mark it with a number in the figure. Compare between the meshes. State that the results will not have a smaller NRMSD unless we know exactly how the bathymetry is treated.}

The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}. The memory requirement varies from $0.5-558.5\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use?}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use?}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 & 3527 & 437.8 & 4539474 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\imycom[RR]{tested some new mumps parameters, still no consistent benefit, but the best run was about 15\% faster now and slightly less memory required as I removed some unnecessary interpolation-varaiables overhead}

\section{Discussion}
%
% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
%
% In order to make your discussion section engaging, you should include the
% following information:
% - The major findings of your study
% - The meaning of those findings
% - How these findings relate to what others have done
% - Limitations of your findings
% - An explanation for any surprising, unexpected, or inconclusive results
% - Suggestions for further research
%
% Your discussion should NOT include any of the following information:
% - New results or data not presented previously in the paper
% - Unwarranted speculation
% - Tangential issues
% - Conclusions not supported by your data
%

@@

@@

The real MR3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data. Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem. We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes. Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general. The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
\imycom[RR]{9M real valued vs. 4.5M complex-valued, what is correct here? Anyway, we should also state that even emg3d uses 6M only for the same setup, so why did they (over?)discretized this model so excessively?}
\imycom[DD]{Add a note that the custEM/PETGEM mesh can handle the entire survey, not just this inline/broadline.}

@@

The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types. In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d. Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain. As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d. For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resitivitiy distributions and cell/element sizes/shapes. This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?}

@@

The shown examples consider the geophysical problem of marine CSEM with resistive bodies. We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography looking for conductive bodies. The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks. The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
\imycom[RR]{changed last sentence to mining + environmental for custEM (actually we will focus way more on gorund/salt water investigations now at LIAG)}

@@

\itodo{Discussion poins from Evert: How can you attribute differences to the solver? There are mesh element effects as well and the way Maxwell's equations are discretized plays a role too.}
 We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
\section{Conclusions \& Outlook}
%
% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
%
% Your conclusion should:
% - Restate your hypothesis or research question
% - Restate your major findings
% - Tell the reader what contribution your study has made to the existing
%   literature
% - Highlight any limitations of your study
% - State future directions for research/recommendations
%
% Your conclusion should NOT:
% - Introduce new arguments
% - Introduce new data
% - Fail to include your research question
% - Fail to state your major results
%

We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model. All comparisons exhibited an excellent reliability of the solutions.\imycom[RR]{reliability of overall $\approx$1\% misfit for layered and blocky test model and $\approx$10\% for realy world model.} Our data should make it very easy for new codes to have a readily available data set to test against and validate. We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.

>>>>

The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well log data a realistic, three-dimensional resistivity model with vertical transverse isotropy (VTI), called MR3D, which they released under the open creative common license \emph{CC BY 4.0}. \cite{GEO.19.Correa} computed CSEM data for MR3D for six frequencies from 0.125\,Hz to 1.25\,Hz, and released them under the same CC license. To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}. It is therefore on one hand an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code. On the other hand it is impossible to reproduce it exactly, as it is a closed-source code and we cannot know exactly what was done internally. Additionally, that code is a time-domain code, including the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}, whereas the four codes under consideration here compute the results all in the frequency-domain.

@@

The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside. The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
%
\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines). The grey lines under the coloured lines are not visible in most areas, meaning they are very similar. However, there are three notable zones, (1) to (3), which are explained further in the text.}
%
Two datasets were published, one containing clean responses, and one where realistic noise was added. For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m. It can be seen that the grey lines are not visible for most parts, which means that the data agree well. However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
\begin{enumerate}
  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components. The differences are related to the bathymetry. And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally. See the discussion around Figure~\ref{fig:results-marlim_survey}.
  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level). The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain. This explains their smooth behaviour, without saying anything about their accuracy.
  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all. In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component. The published responses are not stable either, and therefore any of the responses is as bad as the other. Also, tiniest differences in meshing will have a huge effect here.
\end{enumerate}

Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
%
\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively. Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
%
A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less, particularly for the inline $E_x$ component it is only a few \% or less. In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., negative offsets in the inline and broadside $E_x$ responses, in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD. Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.

@@

The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
%
\plot*{results-marlim_entire}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the entire computational domain.}
%
The top rows show the tensor mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem. The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.

\itodo{We have to decide which figures to include, please state your preference:
\imycom[DW]{I would go for at least two figures, probably 9 and 10 (in reversed order); in my opinion these are the most interesting figures, and I have never seen a comparison like this.}
\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
}

%
\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}

The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model. At, e.g., two kilometers below the seafloor there are already significant changes visible, purely due to meshing. This is an important insight that has to be taken into account when interpreting inversion results.

The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}. The memory requirement varies from $0.5-520\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).

\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use?}
\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use?}
%
\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
  \centering
\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
  \toprule
  %
       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
  \midrule
  %
  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
  \petgem & 96 & 3527 & 437.8 & 4539474 \\
  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
  %
  \bottomrule
\end{tabular}}%
%
\todo{Update nc-file of custEM for new CPU/RAM.}

\section{Discussion}
\imycom[DW]{Currently still a collection of discussions. Needs better structuring.}

@@

For the MR3D results one might argue that 5-10\,\% NRMSD is a lot. We argue that this is probably as good as it gets, given that the code with which we compare is not open-source. This has been shown within the process of these results. Our first attempt were based on the originally published, fine MR3D model. This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation. However, none of the codes were able to reproduce the published results. The reason is that there are many ways how you can extrapolate a model. We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model. It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.

@@

The real MR3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data. Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem. We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes. Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general. The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices. It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.

@@

The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types. In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d. Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain. As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d. For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resistivity distributions and cell/element sizes/shapes. This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?
\imycom[DW]{If this is true we should definitely include it. However, this is new to me (and I currently doubt it), we would need a reference confirming this.}
}

@@

The shown examples consider the geophysical problem of marine CSEM with resistive bodies. We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography looking for conductive bodies. The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks. The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).

@@

We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.

\section{Conclusions \& Outlook}
\imycom[DW]{Not really conclusions, but a mix with discussions. Make pure conclusions.}

We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, a model containing three resistive blocks, and the realistic marine Marlim R3D model. All comparisons exhibited an excellent reliability of the solutions, in the order of $\approx1\,\%$ misfit for the layered and the block model, and $\approx10\,\%$ for the real world model. Our data should make it very easy for new codes to have a readily available data set to test against and validate. We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
